\chapter{Nursery Rhyme}
\begin{ChapterNote}
``My colour is black to the blind, but the blue and gold are seen of the seeing.''
\end{ChapterNote}
\begin{Standard}
Lillian stared at the colorful shortcake before her, vaguely listening in on the
blonde's phone conversation. She'd somehow managed to convince the officer to drive
them to the caf\'e without asking too many questions. Lillian herself had stayed quiet
for the entire trip; some part of her didn't want to ruin the blonde's convoluted lie.
In any case, it almost certainly would've been even more trouble to act out in front
of the cop.

``Well I can't tell from just that alone, I'm not psychic.'' The blonde poked at her
own pastry with her fork, a thicker model of smartphone against her ear. ``That's
fine, just...'' She glanced up at Lillian, who met her gaze and quickly dropped it.
``Keep an eye on the others and don't spread too thin. I'll be back in a month at most.''

Lillian glanced off to the side. The caf\'e was empty aside from themselves, and the waitress
had been reluctant to serve them considering they were closing in twenty minutes. The few
businesses that stayed open late were rarely positive to customers that actually came in at
those hours. Lillian had gotten fairly used to the attitudes of overworked employees during
her frequent nightly errands.

``Mhm. I'll look around when I can.'' Lillian still hadn't touched her own plate. She still
didn't know what the blonde's angle even was. Surely, she didn't make it a habit of visiting
a rarely-used bridge nightly just to hear stories of misery and hopelessness. Lillian didn't
understand. She wondered if the girl was just sadistic, or if she was actually trying to kidnap
her.

``That, you can just do what you normally do or whatever.'' The blonde scooped up some frosting
and popped it into her mouth. ``Sure, sure.'' Lillian supposed she was a good target, considering
nobody would come looking for her. The blonde didn't know that, but Lillian was fairly certain
her foster parents, despite being furious and desperate to teach her a lesson for daring to
run away, wouldn't put in the effort to plaster her name and face on local media or draw attention
from the police. And maybe getting kidnapped could be less unpleasant than being moved to more
orphan homes. She was doubtful about that, though.

``If you don't finish that, we're leaving it here,'' the blonde spoke up, apparently done with
her phone, `the fridge in my hotel is messed up.` Lillian wanted to go back to the bridge.
``Helloooo?''

``Why did you bring me here?'' Lillian asked quietly. The blonde shrugged.

``Got rid of the cop for you, also wanted sweets.'' She shoved some more cake into her mouth.
``Two birds.'' Lillian slumped forward and leaned on the table. ``I'm Allison, by the way.
Age sixteen. Friends call me Allie.'' Lillian raised an eyebrow, glancing up to Allison's blank
stare, her fork still in her mouth.

``Nice to meet you...'' Lillian mumbled into her sleeves.

``What's your name?''

``...Lillian.''

``Can I call you Lily?''

``I don't care.'' Lillian continued to stare at the shortcake while Allison ate quietly.
``Can I go now?'' Allison pointed with her fork.

``At least try it?'' Lillian sighed and slowly sat up straight. She picked up the fork and
hesitated. ``I don't think they poisoned it.'' Lillian wished they'd poisoned it.

It was moments like these that reminded her it was all borrowed time. Someone might try to be nice
her, or something not horrible might happen to her, but in the end any moment she wasn't
screaming into the void in her mind was another moment she was dreading the next time
she would be.

She'd long since learned to not fall victim to that type of bait. Bumps
in the road were just that, but Lillian had been rolling downhill for so long. Whether it was
being kicked and thrown into walls or having her head slammed by the toilet seat, or
just being sneered at and called names, she'd always been hanging on that chain over
that pit of lava, waiting for it to drop her in once more.

``Do you like this city, Lily?'' Lillian cut off some frosting.

``I like that bridge,'' she replied bitterly. The sweetness in her mouth did little
to calm her. Allison sighed deeply. It reminded Lillian of the ones who berated her
for being such a downer all the time, the ones who complained about her negativity.
She'd tried being positive, a long time ago, and it hadn't ever helped. These days,
she saved her energy for errands and beatings.

``Excuse me.'' Lillian hadn't noticed the waitress come up to their table. Allison
turned to her. ``I'm sorry but we're closing now, would you like a box for that?''
She gestured to Lillian's plate.

``Yes, please,'' Allison responded quickly.

\fancybreak{* * *}

The sidewalk was empty as the two headed back towards the bridge at the edge of the city.
A few of the streetlights were broken. Every once in a while, a lone car would pass them
by.

``You can stop following me,'' Lillian muttered, ``watching me go off won't be any more
interesting than the others.''

``My hotel's this way too. You can come in for a while, if you want,'' Allison replied,
her expression betraying nothing.

``And you're not trying to \emph{save me?}'' Lillian mocked. ``Maybe you're kidnapping me?''

``If I was, would you care?''

``Nobody else would, so I guess not\textemdash{}'' Her voice broke. ``This is why you like
it, isn't it? Talking to people who have nothing left. It's so easy to mess with them.''

``When you hit the water, it'll really hurt,'' Allison explained calmly, ignoring the accusation,
``and sometimes people survive. And I hear that's the worst thing ever.'' Lillian laughed.

``I'd love that. The biggest middle finger from God, when you can't even off yourself right.''

``I've got a gun in my room.'' Lillian froze and turned to the blonde with narrowed eyes. Allison
met her gaze with a smile. ``Some people who can't aim properly survive that too, but I can show you
how...and if you mess up I promise I'll finish it for you.'' Lillian stared at the girl incredulously.

``What the hell is wrong with you?'' Allison giggled.

``You're not the first person to ask that.'' The blonde yawned and played with her cross.
``I told the others too, that there are less painful, less scary ways. They told me to
go away.'' She started walking again. ``I just think it'd be nice, for it to not hurt
you anymore than you already are.'' Lillian stood in place, watching the girl's back.
``It's up to you, though.''

After a minute passed and it became apparent that Allison wasn't going to turn around again,
Lillian started moving. Her chest hurt now more than ever and a hundred thoughts clouded
her mind. At the very least, it'd be nice, if she weren't alone when it was finally over.

\fancybreak{* * *}

The hotel lobby was empty. Lillian nervously glanced at the cameras in the corners
as she quietly followed Allison into the elevator. The blonde keyed in for the top
floor and the doors closed. Neither spoke during the ride up.

Once the doors opened, Allison walked out and made a sharp left. Lillian followed
closely, staring at the hood of the girl in front of her. They reached the end of the dimly
lit hallway and Allison swiped a card on the door's lock. Lillian heard a click and
Allison swung the door open. The room was fairly spacious, sporting two queen-size beds
and a private bathroom. Scarlet curtains hung over the massive windows and the blankets
were covered in lace designs.

Lillian hadn't paid attention to the hotel's name as they'd walked in, but it seemed
to be very high-end. She couldn't remember the last time she'd been in a place like this.
She walked in cautiously as Allison closed the door behind her, suddenly feeling like
she didn't belong.

``Sit wherever,'' Allison said, moving to place the small box of barely touched cake
on one of the nightstands, ``I was planning on leaving in three days or something
but I guess I'll leave tomorrow morning instead.'' She turned back and went to retrieve
a backpack on a shelf. ``So they don't come looking for me to ask questions.''
She placed the bag on the floor and unzipped it. ``Anyway, just pretend the room's yours.''
Lillian watched the girl dig through her bag as she sat down on one of the beds.
``I can ping the police afterwards if you don't want your body to lie around for too long,
so you look decent for a funeral or whatever they do.''

``Funerals are for the living,'' Lillian mumbled, examining the intricate patterns on the bed.
It was strange to think someone like her would spend her last moments in a place like this.
She suddenly looked back up, wanting to ask about the hotel, about who this girl even was
to have what she did.

Allison pulled out a modern-looking handgun and a long black tube. Lillian suppressed
her shock. It wasn't as if she hadn't seen a gun before, but in that moment she held her tongue,
promptly realizing she didn't actually want the answers anymore. She decided she wouldn't
question how expertly this teenager two years younger than her handled a firearm,
or any of the other strange things about her.

``I'm gonna silence this for obvious reasons. Um, you should go to the bathroom first,
just, y'know.'' Lillian furrowed her eyebrows at the suggestion and sighed. It was
so unnerving to her, that Allison carried these conversations so naturally. She stood up
and headed for the bathroom.

She stayed inside for longer than she'd intended, simply staring into the mirror, at the
burns and scars on her neck, and the bruises around her cheeks. Dull, sleepless, brown eyes
traced the lines in her messy black hair. By the time she shook herself back to reality, she
was somewhat surprised that Allison hadn't come knocking.

Stepping back out, she found the blonde passed out rather inelegantly on the far bed.
The small box on the nightstand was now opened, only a few crumbs barely visible inside.
Lillian stood in silence for a moment. In the past few hours, she'd found there
was something very off about Allison. It was only now that she wondered, if the blonde
cared less about everything than she herself did.

Lillian's eyes drifted to the pistol on the bed beside Allison, now set up with
the silencer she'd been configuring earlier. She looked back over to the girl's
backpack, which was still wide open. A few bottles of white pills were arranged
neatly outside it. Inside, Lillian could make out wrappers of some sort, a few notebooks,
and an empty bottle without a label. She immediately dropped the idea of digging
through the bag and headed to Allison's bed.

She could simply leave now, she realized, but she supposed there wasn't much of a
point to that. After all that had happened, and after every chance she had to leave,
she simply wanted to rest. She briefly wondered why Allison hadn't been the one to get sick
of her. It wasn't as if she'd told her any stories, like she supposedly wanted. Lillian
sighed and poked the blonde in her cheek. Her eyes flickered open and she blinked drowsily.

``A-ah, sorry...dozed off.'' She stretched and sat back up. ``Mmm, gun's ready,'' Allison
began, eyes drifting around the room as if searching for something, before settling on
her bag. ``Oh, right, I also have some cyanide...'' Lillian immediately lied down
onto the bed. Of course she had cyanide. ``And some sleeping stuff. They'd probably
be even better but I figured I couldn't prove what they were to you, that's why
I suggested the gun first.''

``I honestly don't understand you at all,'' Lillian stated, closing her eyes. ``So
this entire time, you were doing the opposite of saving people?''

``Like I told you, I'm not gonna be the one to decide what \emph{saving} even means.''
Allison replied, lying down beside her. ``Don't you think I'd just bring those with me
if I was doing what you think I'm doing?''

``Then why do you have\textemdash{}'' Lillian froze, suddenly recalling their meeting
on the bridge. ``You said you weren't there to jump...'' Allison didn't respond.
``...Are those pills for \emph{you?}'' Allison giggled loudly, burying her face in a pillow.

``Weird conclusion to jump to,'' she said, muffled, as Lillian looked on in confusion.
``They used to be.'' The blonde got up and pulled the gun to her lap. ``This, too.''
Lillian sat up as well.

``So you...used to be like the ones from the bridge?'' she asked cautiously, ``what...made
you decide not to?'' Allison suddenly leaned in with a smirk, making Lillian lean backwards.

``Wouldn't chat with me and now you're asking about \emph{my} story?'' She clicked her tongue.
``Hypocrite,'' she accused playfully. Lillian looked away.

``You don't have to tell me either,'' she muttered, slightly nervous. Allison sat up straight.

``Well they don't work on me. Period.'' She poked at her necklace again. ``I mean stuff like
the gun still hurts, but, next thing I know I'm fine again. Ai won't let me die.'' Lillian
stared at the cross in her hands.

``The angel again?'' Allison shrugged.

``These days, I keep the gun for mercy. I don't know what Ai does to the people who try to
hurt me, but it seems like a bullet to the head is a lot nicer.'' Lillian wasn't sure how
to respond. Allison was clearly unwell. ``Just forget I said anything if you want,''
Allison muttered, ``do you still wanna go through with this?'' She raised the weapon slightly.
Lillian nodded silently, shifting uncomfortably on the bed.

For the next half hour, Allison explained in detail about angles of entry, targets in the brain
and what to avoid, along with common mistakes and consequences of having faulty aim or a shaky hand.
As Lillian listened, she felt like the expertise came from someone who'd tried it themselves. As
the makeshift tutorial ended, the room descended into silence. It was nearly five in the morning,
according to the digital clock on the nightstand.

``Whenever you're ready.''

``...Can I ask you something?'' Lillian stared into her lap. Allison nodded, although unsure
of whether the other girl could see her. ``Why me?'' Allison stared at the pistol for a moment,
before flipping the safety off. She shoved the weapon into Lillian's hands.

``If that's your last wish, I may as well show you. Or try to.'' Allison stood up off the bed and
walked to an open wall. Lillian watched in confusion. ``I can't convince Ai to show herself to anyone,
I don't even know if she can.'' The blonde leaned against the wall and planted her feet firmly on the ground.
``But I \emph{know} that the people who try to hurt me see \emph{something.} Shoot me in the leg, and you have
to \emph{mean it.} Then I'll explain.'' Lillian dropped the gun to her lap.

``What? No!''

``You're gonna keep thinking I'm crazy until you do this. Please. Just aim for my leg,'' Allison tried
to assure her, ``we'll both be fine.''

``I didn't come here to \emph{shoot you!} What is \emph{wrong} with you?'' Lillian nearly shouted.

``You came here to \emph{shoot yourself,} what difference does it make? You don't care about anything
anyway, right? I'm just a psycho brat who interrupted some weakling's last day on Earth!''

``\emph{Shut up!}'' Lillian raised the pistol violently, arms trembling. Her mind raced. Her finger
pulled against the trigger as she mentally screamed at herself. She felt all the night's pent-up
frustration bubble up to the top. This arrogant lunatic of a girl showed up out of nowhere to make
a simple night so obnoxiously complicated.

And then she threw the gun to the ground.

It landed with a loud clatter and she buried her face in a pillow behind her, trying to hide
her crying. A few minutes passed before she felt weight on the bed again.

``Guessing you didn't see anything, then.'' She didn't respond, and the blonde sighed.
``I \emph{can't} die. So I run around in circles, looking for good reasons \emph{not} to die.''
Allison paused. ``They say a decent number of people use that bridge. So I started stopping by,
wondering if I'd find someone who might wanna look with me.'' Lillian felt the blonde lie down beside her.

``Why you? I listened to so many stories, but I felt like you were the first that
might listen to me, too.''
\end{Standard}
