\chapter{Little Star}
\begin{ChapterNote}
``Do what thou wilt shall be the whole of the Law.''
\end{ChapterNote}
\begin{Standard}
It was around one in the morning by Lillian's guess. The chill of the night air
pricked at her. Her nylon jacket, even if it wasn't as torn up as it was, did little
to protect her. Shoving her hands deeper into the pockets of her jeans, she walked a
little faster as the view of the bridge came into view. She glanced absentmindedly
at the blurry reflections of the stars in the water.

Lynn was a quieter coastal city. Although brimming with activity during daytime,
fairly few places would stay lit up late after night fell. The lack of light pollution
meant a fair amount of starlight reached the citizens, for those willing to stay up
every now and then. On the other hand, the low number of witnesses also often invited
trouble, which kept many from actually doing so.

As Lillian approached the mouth of the bridge, expecting an empty scene like the last
couple of times she'd passed it at this hour, she noticed a hooded figure near the center
of it. She stared blankly before registering that today might not be her day. Her heart fell,
She really didn't want to spend another day at home.

The figure hadn't moved an inch yet, seemingly staring at something in the horizon.
She exhaled gently and began walking down the bridge. She was tired. She was far too tired.
She didn't particularly care whether this was some stargazer or an escaped convict.
Maybe she would chat with the stranger, spew out some half-hearted small talk from
what little she could squeeze out of her soul. Maybe she could convince them to leave, or just
wait until they chose to. They wouldn't stand there until morning, but she herself didn't
have anywhere to be.

But as Lillian got closer to the person in the dark blue hoodie, she realized this stranger
was not standing at all; they were sitting rather precariously on the metal railing of the
massive bridge. It was at this point that the figure turned to her. Lillian stared back at the
face of a girl who was no older than she was. The girl on the railing kicked her legs forward
off the edge of the bridge and leaned back at the same time to maintain her balance. She tilted
her head as Lillian half-expected her shoes to drop off into the water below.

``Here to jump?'' she questioned. Lillian stared back silently, wondering what this girl
was trying to do. She shook her head in response and continued walking. She took up a position
about a meter from the other girl, noticing her return to sitting normally out of the corner of her eye.
Lillian leaned forward on the railing.

``Just stargazing,'' she replied softly. The other girl didn't respond. Lillian sighed quietly.
The fact that this girl could easily fall off the railing at a moment's notice made her feel
as if they were both here for the same reason, but she didn't feel like risking the off-chance
the girl was here to play hero instead.

``Did you know how far away stars really are?'' the girl asked. Lillian continued to stare
at the night sky. The pinpoints twinkled weakly. ``Even if they all disappeared, right now,''
she mused, ``we wouldn't even notice for hundreds of years.'' Lillian stayed silent, not
really processing the girl's words. She wanted her to leave, but didn't have the energy to
think of anything.

``You should get down from there, you might fall off.'' And so she settled on humoring the girl
until she got tired and went home.

``I hope not.'' Lillian noticed a sudden motion in her peripheral and turned. Her heart skipped
a beat as she watched the girl abruptly slide off the railing entirely. She rushed over to
where the questionably insane teen had been, almost tripping in her shock. The girl's
fingers still hung onto the railing, and Lillian looked over the edge with wide eyes.

``It's a really long way down, I hear it hurts a lot even if it's just water.'' The girl
recalled thoughtfully, apparently gauging the distance to the lake. She promptly glanced
back up, meeting Lillian's somewhat horrified gaze. ``What? See a ghost?''

Lillian quietly backed away as the girl, with some effort, pulled herself back up and
sat back down onto the railing, this time facing away from the water. She swung her legs.
The wind had blown her hood back, revealing shoulder-length blonde hair. Her zipper was
only halfway up her stomach, and a black cross with silver trim hung around her neck.

``...Are \emph{you} here to jump?'' Lillian finally asked, wondering why she was
shaken up by something she came here for herself.

``Hm? Not really.'' Lillian raised her eyebrows at the strange answer. ``Oh, I get it,
sorry if that surprised you.'' The girl ran a hand through her hair sheepishly.
``Sometimes I do things most people wouldn't think of doing.'' She poked at the
cross around her neck. ``See, I have an angel watching over me. So I kinda sorta
stopped caring about what \emph{dangerous} means a while ago.''

Lillian blinked twice, and then rubbed her eyes in exasperation. She walked up to
the railing beside the girl, crossed her arms on it, and buried her face in her
worn jacket's sleeves. She almost would have preferred the escaped convict over this
lunatic. A few moments of silence passed.

``Do you believe in God?'' the girl eventually asked. Lillian thought of the time
she'd spent shivering next to an alley dumpster, the time she'd spent fruitlessly
trying to defend herself from the other orphans in foster homes, and the time she'd
spent as nothing more than a slave for her new parents to order around and beat
into submission.

She thought of how desperation drove her to pray to the mystical man in the sky.
She'd begged and pleaded, with every new foster home, every new officer or social
worker that promised her safety and delivered lies, for something divine to come
take her away. And in the end, she had to do it herself.

``Not at all,'' she choked out in a broken voice. She steadied her breathing.
There was no real need to break down in front of the lunatic church girl. And
at this point Lillian was fairly sure the girl was in fact here to play hero.

``Good. Then you don't believe in an afterlife either, right? Heaven and all that?''
It was a decidedly strange thing to hear, coming from a church girl possessed by
an angel.

``Careful what you say,'' Lillian began bitterly, ``your priests might kick you out.''
She heard the girl giggle.

``I don't do church. This necklace was just a present from my father.'' The girl gave
the chain a twirl. ``I just listen to what Ai tells me, never read any bible or anything
\textemdash{}oh, Ai's what she told me to call her, my angel friend.''

``The voice in your head, right.''

``Not really a voice, Ai doesn't actually \emph{talk}\textemdash{}well, you're just
making fun of me anyway, but it's okay.'' At that, Lillian turned to glance at the girl,
who simply smiled back. ``I don't mind if you think I'm crazy, but I still wanna tell you,
if Ai is right\textemdash{}and I think she is\textemdash{}there's nothing waiting for us
out there anymore.'' The girl swung her legs over the side again and faced the water. ``We just
stop being. Nothingness. So all the people who try super hard to \emph{impress God} or whatever,
instead of making the best of their time\textemdash{}''

``And when there's nothingness here either, nothing to make the best of, and you're \emph{sick and tired}
of trying and hoping?'' Lillian interrupted angrily. The other girl was silent. Lillian
coughed to clear her throat. ``Look, I know what you're trying to do, but I'm not
here to jump. You can just go home now.'' The girl swung her legs again.

``Can I ask who gave you those bruises?''

``No.'' Another minute of silence passed.

``I met lots of people on this bridge in the past month.'' Lillian rolled her eyes.
``People older than me with cuts on their wrists. People younger than me with black eyes.
People with burns and bruises like you.'' The girl paused. ``A few actual stargazers.''

``Look, you.''

``Aside from the ones who brought telescopes, nobody's ever waited this long for me
to be the one to leave first.'' Lillian turned to her with a weak glare.

``So how many did you save?''

``I'm not here to save people, just to talk.'' The girl stretched her arms and fully
stepped down from the railing. ``I was bored. No clue what happens to them after,
aside from the few that jumped off in front of me.'' She yawned. ``Hope they don't
regret whatever they chose, though.'' Lillian stared into the water.

``I...''

``I want cake. There's like one cafe open this late, you wanna come? My treat.''

``Wh\textemdash{}'' The girl gestured and Lillian's rejection hung in her throat
as she heard tires roll up behind her. The flickering lights of the police car cast
writhing shadows over the concrete.

``You girls alright? Shouldn't be out and about this late!'' the officer shouted,
leaning on his car door.

``Yes sir, just watching the stars!'' Lillian watched the girl pass her as she felt
her heart sink. She wondered how it had turned out like this. Exhaustion and pain
spread from her chest. ``C'mon sis! Mom's waiting at the cafe!'' the girl called back.
\end{Standard}
