\chapter{Caged Bird}
\begin{ChapterNote}
Southern Lausanne, France
\end{ChapterNote}
\begin{Standard}
The blonde girl coughed again and cursed under her breath. She was fairly certain
her left leg was fractured somewhere, and her organs wouldn't last much longer due to the
recoil of what she had to pull earlier. She leaned against the
left wall and one of her escorts stopped beside her. A loud crash resounded through
the halls. The lieutenant signaled to the four taking point. The frontliners gestured
between themselves and moved down the right while the rear approached from behind.

``Ma'am, we need to keep moving,'' the lieutenant stated. ``If you need help\textemdash{}''

``Let me borrow the rifle the corporal picked up, I'd be getting in your way if
one of you had to carry me.'' The girl pushed against the wall to balance herself
and glanced at the cross around her neck. In her current state, it'd be troublesome
to engage any hostiles herself, which meant she'd need the rest of her temporary
team to pick up the slack, at least until they found what she'd dragged them here for.
She heard a few clicks as the corporal moved up from behind her.

``Almost full clip, safety's on.'' He handed the rifle to her. She took the weapon
with her left hand, ignoring the pain spiking up her right arm as the heavy rifle
tapped the sling of bandages. With some trouble, she swiftly extended the stock as
far as it could go and repurposed it as a crutch.

``Good enough. Let's go.'' She started towards the end of the hall, where their frontline
had made a right. Her escorts followed silently. This team was what remained of the
platoons she was sent out to support. It wasn't the first time these soldiers had
worked with an inquisitor, so they knew better than to underestimate the girl who,
in the eyes of the uninformed, would appear to be an injured high schooler in church
robes leaning on a Type-63. The inquisitor herself knew however, that at the moment
she may as well have been exactly that.

\fancybreak{* * *}

There was gunfire and shouting at some point, but the girl was more distracted with
trying to ignore her failing body. She gestured forward nonchalantly to let the rear
know they should move ahead. As per the lieutenant's order, only the corporal stayed
behind with her.

``I can lift you if you need me to?'' the man asked in concern, the sentiment
slightly dampened by the voice modulator in his helmet. The girl briefly gave him
a glare before turning forward again. ``You've slowed down a lo\textemdash{}''

``Corporal, if you want in on the action, you can go on ahead too.'' The man sighed.

``You're injured, you shouldn't be alone, ma'am.'' The girl coughed into her shoulder,
leaving a dark red stain on her cloak.

``Then keep your hands on your gun and guard me,'' she muttered. ``And for your
information, I'm dying, so quit wasting my breath.'' The two continued down the corridor
in silence, the girl picking up her pace and gritting her teeth.

\fancybreak{* * *}

By the time the team had regrouped fully, the gunfire had died down. Their side had
sustained no injuries, but four German soldiers had been killed while the rest had
retreated further into the facility. Two German scientists sat slumped against the wall,
their hands tied together, shouting something at the lieutenant despite the fact he clearly
wasn't listening.

``Well, this should be the wing we want, if that floor map was right.''

``The hell are we looking for again? A patient?''

``A test subject. This is a research facility,'' the girl corrected. ``Check all
the rooms along this hall, loop over into the next one if you need to.'' She heard
one of the scientists mockingly mention something about child soldiers which she
ignored. One of her soldiers promptly told him to be quiet, though the language
barrier clearly made all these efforts pointless unless she herself was involved.
She coughed again as the lieutenant asked them to split into teams of two. ``You're
looking for a girl my age, probably older. Albino. White hair, violet eyes.'' A few
of the soldiers turned to her at this. ``...I assume you won't miss her.''

As the teams set off, the lieutenant stayed with the girl to watch the scientists.
They simply stayed silent, staring at the bodies of their comrades at the far end
of the hall.

``Surprised nobody got hurt,'' the girl mused as she shifted her weight between
the rifle and her right leg to distract herself.

``There were only six of them,'' the lieutenant replied. ``Given it's a research
facility, explains the low security.'' They were deep in enemy territory, and
on very thin ice because of it; the enemy had forced them to flee straight into
occupied Lausanne and they were cornered. If the girl she was looking for wasn't
here, they'd all be corpses very soon. The only advantage they had was the fact
that the Germans stationed here weren't expecting enemies at all.

``By the way, don't let your guard down. The ones you let escape will be back with
plenty of friends, given the...nature of the work here.'' The girl spun the rifle
barrel into the metallic tiles below.

``Which would be...?'' the lieutenant trailed off, uncertain. The girl sighed.

``The documents we have will be submitted to the Vatican for review,'' she explained.
``The less you know about this stuff, the better.'' The officer shrugged.

``Not much would surprise me after what I've seen with you inquisitors.'' The girl
laughed a little before coughing violently into her shoulder. The scientists had turned
to her and she glanced back, uninterested.

``You want hostages?'' she inquired.

``Does the Vatican need info?'' he countered. ``Depending on how this goes, we could
bring them back if you're...\emph{up for it,} but\textemdash{}'' The walls shook
as muffled explosions sounded out in the distance. ``Are they seriously \emph{bombing}
their own facility?'' The girl clicked her tongue.

``The ones chasing us probably think this is just some abandoned mining tunnel,'' she
muttered. ``Tell them to hurry up before they bury us.''

\fancybreak{* * *}

The first few rooms had been empty, with track marks faintly visible on the otherwise
spotless flooring. It seemed like they had noticed the intrusion and were looking to
evacuate the entire wing. The girl counted herself lucky that they hadn't quite gotten
to her target. One of the teams had called in a positive; a bedridden albino who wasn't
comatose like most of the other occupants that remained.

The girl had left the lieutenant with their hostages and her eyes searched for the
door number she needed. Another, particularly heavy explosion shook the site and the girl
leaned against the left wall for support. She wondered if the entry was caved in yet.
It'd be a blessing for them, since they'd only need to deal with the facility guards.
On the other hand, if the site's personnel got out word that the cave itself was an allied
structure and their pursuers came in the front door, they'd be fighting on two fronts
instead.

A crash drew her attention. Another German scientist; a woman in a lab coat, burst out
from a door further down the hall and scanned the corridor, quickly meeting the girl's
eyes. She drew a black revolver and the girl struggled to raise the rifle using the
wall as leverage. As she flipped the safety, the scientist's bullet clipped the wall
beside her, sending her ears ringing. She fired again, and so did the girl.

The scientist's head whipped backwards from the rifle round. Her body fell to the floor
as multiple teams exited from doors in front of her. The girl lowered her rifle to the
ground and leaned on it once more, the shimmer in the air dissipating. She coughed
loudly, staining the floor red, and glanced off to the far right wall where the bullet
had deflected.

``Damn, nice aim!''

``Why are you idiots \emph{touring the place} instead of standing guard outside?''
Another explosion shook the facility.

\fancybreak{* * *}

Once the team reorganized, the explosions had stopped completely, which the blonde
had quickly pointed out was likely a bad sign of things to come. She now stood in
what looked like a hospital room with the corporal and two others while the rest
were either standing guard or securing the remainder of the wing. The albino
was lying flat on her bed, with several IV drips and medical monitors attached
to her chest and limbs. She stared straight up at the ceiling, never having
acknowledged the girl's entry, and yet continued to blink. Her chest rose and fell
under the hospital gown she wore.

``Yeah so, she's not a potato like the others since her eyes are open but uh...''
The soldier knocked his helmet. ``I walked in front of her earlier, clapped,
snapped my fingers, shined a light, nothing. Nobody's home.'' The girl walked closer
to the bed and leaned over it, staring into the patient's eyes. The albino was pale,
as expected, though her eyes were colored a bright violet, and the girl could see
faint rings in her irises.

``Any of you know what this is called?'' she questioned nonchalantly.

``What, albinism? Can't handle sunlight, right?''

``Alexandria's Genesis,'' the corporal spoke up, deep in thought. ``A myth of a
so-called perfect being.''

``The hell...? Her?''

``I mean, the kid's drugged up.''

``She's basically braindead, are you sure about this?''

``Gentlemen, you'd better \emph{hope} this works because we're getting closed in
on all sides right now,'' she stated simply before standing upright and then slowly
lowering herself using the rifle. The soldiers stiffened as they watched her lean
the rifle against the nightstand and grip her cross. They had heard rumors, most of
them likely heavily exaggerated, of this particular inquisitor. Those that detailed
her work in the war painted her as a true saint. Those that spoke of the dark contracts
she had to sign for her miracles depicted her as a monster. The remains of the
overwhelmed platoons had so far only viewed her as another soldier, albeit a young
one. Now, they might see her at her worst.

``O Lord in Heaven, I ask of your forgiveness...''

\fancybreak{* * *}

The girl's prayer lasted only a minute, but to the soldiers it felt far longer, in
anticipation of what they knew was about to happen. Regardless of what horrors
the girl on the bed had been subjected to, the inquisitor could have been taking an
innocent life.

The blonde fell to the ground abruptly, her cross clattering against the tiles. The
corporal raised a hand to stop the others from approaching. Only a few seconds passed
before the albino twitched her fingers. She blinked erratically. She coughed. And then
she slowly began to sit up. Her hair, appearing silvery in the light of the panels above,
fell over her right eye and she slowly brushed it away. The trembling in her arms
dissipated gradually.

``Ma'am,'' the corporal stated firmly. The girl stared ahead blankly. The corporal
cleared his voice. ``Ma'am, please identify yourself,'' he addressed formally, as they
had discussed before breaching the facility. The soldiers at his side tightened their grips
on their weapons in response, remembering the protocol they were told to follow. The girl
blinked again and stretched her neck before turning.

``Right, sorry, bit of a head rush,'' she replied in a weak voice. She began carefully
removing the attachments on her body, ignoring the monitors' distressed complaints.
``I am...'' She pushed the blanket off the bed. ``Saint Allison of the Vatican's Inquisition,
western branch.'' It was the same greeting she'd used to introduce herself when she'd
first arrived. ``And I,'' She finished with the last IV drip and swung her legs off the bed.
``Happen to be...'' She grunted while reaching for the device in the blonde's inner pocket.
``A bit of a monster.'' She swiftly entered the passcode and turned the screen to the team,
displaying a pulsing blue map of the surrounding region. ``Right?''

The corporal nodded and offered a salute reflexively. The others followed, still
somewhat bewildered.

``So that's it then...?'' Allison smirked and shrugged.

``Well I'm sorry if you were expecting more but,'' She stepped off the bed and got
to her feet, swaying slightly. ``There's not gonna be fireworks or anything.''
She crouched down. ``Now get out and check on the lieutenant, I need a minute to change.''
The soldiers looked at each other and slowly complied. Once she was alone, the girl
glanced at the corpse on the ground. A pool of blood was forming, although very slowly.
She pulled the cross off the blonde's neck and sighed, wondering if there'd be time
to bury the body.

\fancybreak{* * *}

The gunfire outside started just as Allison finished wrapping the body in the blanket.
The blood was seeping through faster now. The corporal knocked loudly against the door.

``Ma'am!''

``Yeah, I'm coming!'' she shouted back, letting the body float gently beside her.
The rifle clattered across the floor to her hands, before she decided it was too
much of a hassle and let it fall once more. She promptly opened the door and saw
one of her own go down as the rest retreated past her. Bullets flew at her, sparking
against the shimmering air. She skipped out into the middle of the hall, standing between
her team and what seemed to be a specially armored German squad. The bullets picked
up in frequency and continued to bounce off of nothingness as the enemy began taking
steps back.

\emph{``Gentlemen,''} she shouted in German. \emph{``This is an experimentation
facility, yes?''} She raised her hands to her sides in welcome. \emph{``I am what
you might call...irony.''}
\end{Standard}
