\chapter{Homecoming}
\begin{ChapterNote}
Vatican Greater Audience Chamber, District XIII, Italy
\end{ChapterNote}
\begin{Standard}
The squad that Allison had brought back ended up losing a total of two soldiers
between the time they'd first arrived at the German research site and their return
to allied territory. Considering how far into France they'd been, she considered
the operation decently successful. The cardinals seemed to disagree on that note.
She wondered if they'd get some leave for their troubles, as she herself would be
seeing no such thing.

``Saint!'' Allison glanced up at the second seat. Aside from the decorative pillars
and mosaic ceiling, the debriefing room was painfully plain in the girl's opinion.

``Yeah, can I leave yet? I need to take a shower; smell like hospital.'' She brushed
her hair backwards, noting it was still very much tangled up. A few cardinals leaned back
in exasperation, letting the lights behind them bounce off of the glass panels separating
them from her.

``This is a serious matter, Saint,'' the fourth seat began. ``Your actions have cost us
what could have been a massive advantage in the war.'' She rolled her eyes.

``Look, I really don't understand why you're all so upset, I was ordered to support
our troops on the western front because \emph{supposedly} the Reich got a hold of
some messed up stuff.'' She stared at her fingernails, noting they were a bit too long.
``I did all I could, brought you back the relic plus everyone I managed to drag out of the
hellhole the\textemdash{}''

``You \emph{abused} classified intel, led a disorganized, \emph{vastly understaffed} squad
of injured soldiers \emph{without authorization}, deep into enemy lines and attacked
a high priority target which you were well aware there are plans to capture \emph{fully} during
a future offensive.'' The second seat paused only a moment and then made to continue, but
Allison jumped on the brief silence.

``First of all, you were going invade the place anyway, I just did it earlier as part of
a detour and saved you some trouble. We brought back bags of documents and some of their
test subjects too. Far as I'm concerned, everything turned out alright.'' The second seat
slammed his fist on the desk.

``And everything you \emph{didn't} bring back?'' he shouted angrily. Allison shrugged.

``We could only carry so mu\textemdash{}''

``Therein lies the problem, Saint. If we had kept our intentions secret until our offensive
against France, we could have collected plenty of valuable information.'' The fourth seat rubbed
his temples. ``What you did manage to gather is negligible compared to that. This is
a lost opportunity of great scale, do you understand?'' Allison sighed, supposing it'd be
difficult to talk her way out of this line of thinking.

``Alright, how about this; we were deep behind enemy lines because we were \emph{chased there.}
No chance what was left of that platoon could handle being surrounded like that, but guess who
can?'' She raised a finger in mock understanding. ``Oh that's right, me! But after the tanks
and helis and the damned relic, I was down an arm, limping, and fighting back organ failure.
Excuse me for my emergency detour off the \emph{road to hell}, but I decided to be \emph{resourceful.}''
She lowered her hand and leaned forward. ``If we didn't do what we did, we'd \emph{all} be dead.
And I don't mean to be arrogant but the last time an exarch was K.I.A., we lost half the eastern front
plus twenty supply points off the break in our lines and the relic they stole; it took us
months to recover.'' She took a step back. ``How about you be grateful we pulled
\emph{something} out of this mess?''

The cardinals were silent. Allison stared back, her expression blank. The first seat slowly
leaned forward onto his clasped hands.

``Considering this debriefing has spiraled off-topic, I'm going to ask we stop here.'' He cleared
his throat. ``Any objections?'' The room was silent again. ``Then Saint Allison, we have
another task for you.'' She tilted her head.

``So soon?''

``You seem convinced the inquisition is vital to our chances in this war.'' Allison sighed.
``I'm giving you a chance to prove it. The Reich has supposedly uncovered something in the
Arctic circle. You'll be given details later.''

``Wonderful, I love the cold,'' she droned, turning around and making for the exit.

``And about your body...'' She stopped and adjusted her cloak.

``If you want testing, I'll only consent to minor stuff.'' She turned her head slightly.
``Unless you enjoy making those calls to hospitals and orphanages, I'd suggest
we keep this one going for a while.''

``...Ask for some dye and lenses from R\&D.'' He coughed. ``We'll discuss what you
\emph{brought back} when you return.'' Allison made a half bow and turned towards the
exit once more.

``\emph{If} I return,'' she dutifully corrected.

``One last thing, Saint!'' Allison froze again, holding back a sharp exhale.
The voice of the seventh seat was female, belonging to a weathered woman whom
Allison had bestowed the title of least annoying among the Vatican's brass.
``...Thank you, for bringing them and yourself home safe.'' The violet-eyed
inquisitor smirked and swiftly swung open the massive chamber doors.

\fancybreak{* * *}

``Why are you here,'' Allison monotoned. ``I heard we were scattered to every corner
of the globe.'' The redhead's expression changed from confusion to excitement in the
blink of an eye.

``It \emph{is} you!'' Allison rolled her eyes as she stepped off of the elevator.
Her colleague fell in line beside her. ``I only got back a couple days ago,
they said you radioed in for pick-up after dropping off the grid for a week.''
Allison stared down a few passing officers as the other girl spoke. The military
presence at the Vatican had been growing a little more every single time she'd returned
for debriefing. She caught a few reluctant salutes from the ones who met her eyes
and had bothered to glance at her emblem.

``Been a long week,'' Allison muttered, turning instead to glance at her friend.
Charlotte was one of the few people who had gotten used to Allison's
special circumstances. Security protocols at the Vatican had entire clauses
in place specifically because Allison was a frequent visitor, although not by choice.

``I can see that...how're you feeling? And why do you smell like bleach?'' Charlotte
questioned with a grin.

``Random drugs the Germans injected. Need a shower.'' Charlotte raised a finger.

``Oh hey, is it true you swatted jets outta the sky with their own tanks?'' she
asked thoughtfully. Allison narrowed her eyes.

``Rumors will be rumors, huh? Sure, let's go with that.'' Allison raised a hand
to her forehead and then rubbed her eye. ``They also bombed the hell out of us
and I nearly died. We got caught up in the pincer before they decided to pull
out from our main force.'' The two came up to the corridor entrance for the
residential wing. The security officer checked their IDs and then held the door
open.

``Y'know, most of 'em are saying you're the reason we didn't lose Geneva.''
Charlotte mused with a smile. ``We ended up pushing the line forward instead!''

``And yet the cardinals are still \emph{displeased with my performance,}''
Allison replied, making air quotes with her fingers.

``Ah screw those old geezers, they're never happy anyway. Y'know last week even
Julian told me they were getting on his nerves? \emph{Julian!}''

``Ah yes, the biggest suck-up,'' Allison monotoned. She shook her head and sighed
as they approached another elevator. Charlotte tapped the button for her.

``Anyways, I'm glad you made it back. When they told me you were M.I.A., I wasn't
actually that worried, and look, I was right!'' Charlotte beamed as they entered the
elevator.

``Wow, thanks, that makes me feel great,'' Allison droned in response, keying in
the eleventh floor. Charlotte laughed.

``I mean, you always make it back,'' she pointed out.

``Mm, was close this time. Bastards retreated and took us with them like a fish net,
drove us into France.'' Charlotte seemed surprised at this. ``If I hadn't...''
Charlotte waited for her to finish, but she didn't.

``Then...I'm glad you're safe.'' Allison nodded quietly as they exited the elevator.
A few moments of silence passed as the two made their way to Allison's unit.
``...By the way, love the eyes.'' Allison scoffed and stopped walking, prompting
Charlotte to glance over in confusion. The albino stared back at the redhead
without saying anything. Charlotte furrowed her brows. ``...Hello?''

``Just giving you a good look.'' Allison ran her hands through her hair, which reminded
her it was still very heavily tangled. ``I stand out too much like this so they want
me to wear lenses.'' She started walking again.

``Aww...that's such a waste,'' Charlotte whined as she caught up.

``Need hair dye too.'' Allison raised a finger to her lips in thought.

``So blonde and blue eyes again?'' Charlotte proposed. ``Might help people
identify...well, hm.'' She scratched her head. ``...Oh, by the way, remember what
Aria said?'' Allison rolled her eyes.

``No, they did not \emph{shoot me less} because I was blonde.'' Charlotte snickered.

``I figured. I bet they'll start shooting us \emph{more} since every time we show up,
they end up running home crying.''

``We're still barely holding it together, you know that?'' Allison pointed out as they
approached her unit's door. Charlotte shrugged.

``It'll get better once we figure out what they're doing with the relics.'' They stopped
in front of the door and Allison tapped her card on the scanner.

``So shower, then I pass out and then...'' Allison clicked her tongue. She wasn't
looking forward to another briefing. She supposed she could sleep more on the plane,
depending on how many troops were being assigned to her. Perhaps she'd be lucky
and they'd send her in alone, or perhaps she was overestimating herself because
of this recent acquisition.

``Hey, um...'' Charlotte played with her fingers, staring at the door frame.
``There's a nice cafe that opened up at the edge of District Two...do you wanna
go tomorrow?'' Allison simply stared back, still partially leaning on the door handle.
``It's just, y'know, it's been a few months...and all of us are always hopping
countries, not knowing if we're even coming back...''

``Are you asking me out?'' Allison put on a playful smirk. Charlotte suddenly put
both her hands on Allison's shoulders, causing her to grab the other side of the
door frame for support.

``Please?'' Allison sighed.

``Listen, world's at war and the Reich's trying to pull something again, so they
really want me out there ASAP.'' Charlotte weakened her grip and slowly let go.
``I'm sure you have something they've been asking of you too.'' Charlotte
nodded quietly as Allison opened the door fully and stepped inside.

``...But screw those old geezers, right? Stop by Lab Six tomorrow at nine or so,
we can go after I get \emph{makeup}.'' Allison gently closed the door on
Charlotte's surprised expression.

``...Thanks, Allie!'' Allison leaned on her door, listening to her friend's steps
fade away. She exhaled sharply. Charlotte had watched her swap faces four times,
and yet she never treated her any differently. Allison stared at her reflection
in the mirror to the right of the entryway. She supposed some people had
strange taste.

``She seems so sure of who I am...'' The girl whispered quietly into the mirror.
``Even if I...''
\end{Standard}
