\chapter{In Memoriam}
\begin{ChapterNote}
Inquisition Dormitory Unit 1119, District XIII, Italy
\end{ChapterNote}
\begin{Standard}
\emph{``Just...promise me you'll stop them...from hurting anyone else...''}

Allison's eyes flickered open. Her digital clock read 3:07 AM. Her vision
quickly adjusted to the darkness and she turned over in her bed, once again
half-wishing their rooms didn't need to be windowless for security reasons.
She liked seeing the moon.

She supposed she'd gotten the girl some revenge, though it hadn't seemed like
the girl even wanted that at the time. Allison had torn the site apart in the end,
not having brought that bit up to the cardinals as it didn't make much difference
whether what she left behind was migrated away or burned to ash. They would've
been equally upset with her.

She sighed. Sometimes she wished she didn't end up doing everything she did.
And then she'd question why she felt like that. At least, if her predictions were
accurate and she wasn't too reckless, all that would end here, thanks to her little savior.

Her name was Isabelle Chartreux. Allison remembered all their names, figuring
it was the least she could do. Allison had saved many troops from the German offensive
at Geneva that week, but she was certain Isabelle had inadvertently saved even
more people from her.

``All you can do is your best, huh...'' She closed her eyes once more. ``A sad world
written by a sad God.''

\fancybreak{* * *}
% Head to R&D in the morning, chat with doctor for check-up/hair dye, discuss past, bodies, etc
% Don't ask questions protocol, overview of clearance levels, ethics, etc
% Date should be next chapter
\end{Standard}
